Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-01 R0V0.tex
Improve the part regarding the scalable diagonal optimization. What I need to show is that, if F is sdd than the algorithm provides a basis of monomials to show that F is negative definite

\begin{proposition}\label{prop:}
	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
\end{proposition}

@@

  	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
  	\begin{equation*}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]}\;.
	\end{equation*}
	This concludes the proof.
\end{proof}

@@

Although the decomposition of the MI~\eqref{eq:MI formulation} into smaller components can distribute the burden of computation. These components (matrices) may still have a large dimension. However, by employing an appropriate choice for the basis of squared polynomials, the dimension of the matrix can be smaller \cite{AhmadiHall2016}. To that end, the following class of matrices is recalled from \cite{AhmadiHall2016}.

\begin{definition}\label{def:}
	a
\end{definition}

>>>>

\begin{proposition}\label{prop:clique tree decomposition}
	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
\end{proposition}

@@

  	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
  	\begin{equation}\label{eq:MIF}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]}\;.
	\end{equation}
	This concludes the proof.
\end{proof}

@@

\todo[inline]{Scalable diagonal dominance}

Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}. The negative definiteness of the $F$ can be shown using sum-of-squares optimization. To this end, a vector of monomials $z$ such that $-z^\top F z>0$ need to be found. This the objective of the remainder of this section.

\begin{definition}\label{def:SDD}
	A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $2|a_{ii}|\geq\sum_{i=1}^h |a_{ij}|$ holds. It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
\end{definition}

The set of dd (resp. sdd) matrices $D\in\mathbb{R}^{h\times h}$ described in Definition~\ref{def:SDD} is denoted by $DD$ (resp. $SDD$). Let $z$ be a vector of all monomials on the variable $x$ of degree exactly $d$.

\begin{definition}\label{def:sdsos}
	A form $p:\mathbb{R}^h\to\mathbb{R}_{\geq0}$ is said to be a (resp. \emph{scaled-})\emph{diagonally-dominant-sum-of-squares} (dsos) (resp. (sdsos)) if there exists a (resp. scalable) diagonally dominant matrix $D$ such that $p=z^\top Dz$.
\end{definition}

Consider the class of polynomials $p$ defined by $\mathcal{S}\mathcal{D}\mathcal{S}\mathcal{O}\mathcal{S}(U)=\{p:p = zU^\top DUz, \text{ for some sdd matrix } D\}$. The feasibility verification of the MI~\ref{eq:MI formulation} over $\mathcal{S}\mathcal{D}\mathcal{S}\mathcal{O}\mathcal{S}(U)$
